%-------------------------
% Resume in Latex
% Author : Binhui Xie
% Website: https://github.com/files/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Binhui Xie} & Homepage: \href{https://binhuixie.github.io}{binhuixie.github.io} \\
  Ph.D. Student, Beijing Institute of Technology & Email : \href{mailto:binhuixie@bit.edu.cn}{binhuixie@bit.edu.cn}\\
  Address:  Room 1106, Central Teaching Building, BIT & Mobile : +86-188-1137-9626 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Beijing Institute of Technology}{Beijing, China}
      {Ph.D. Student in School of Computer Science and Technology, Advisor: Prof. Shuang Li}{Sep. 2019 - Present}
    \resumeSubheading
      {Beijing Institute of Technology}{Beijing, China}
      {B.Eng. in Software Engineering, GPA: 3.5/4.0}{Sep. 2015 - Jul. 2019}
  \resumeSubHeadingListEnd


%-----------Research Interests-----------------
\section{Research Interests}
My research interests are in transfer learning and data-efficient learning (particularly domain adaptation, active learning) and self-supervised learning across visual tasks and domains.

%-----------Publications-----------------
\section{Publications ($^*$co-first author)}
% \textbf{Conference Publications}
\begin{enumerate}
    \item Mingjia Li$^*$, \textbf{Binhui Xie$^*$}, Shuang Li, Chi Harold Liu, Xinjing Cheng. \\
    VBLC: Visibility Boosting and Logit-Constraint Learning for Domain Adaptive Semantic Segmentation under Adverse Conditions, \textit{AAAI Conference on Artificial Intelligence} ({\bf AAAI}), 2023, Washington, DC, USA.

    \item Jiashu Wu, Yang Wang, \textbf{Binhui Xie}, Shuang Li, Hao Dai, Kejiang Ye, Chengzhong Xu. \\
    Joint Semantic Transfer Network for IoT Intrusion Detection, \textit{IEEE Internet of Things Journal} ({\bf IoT}), 2022.

    \item  \textbf{Binhui Xie}, Shuang Li, Fangrui Lv, Chi Harold Liu, Guoren Wang, and Dapeng Wu. \\
    A Collaborative Alignment Framework of Transferable Knowledge Extraction for Unsupervised Domain Adaptation, \textit{IEEE Transactions on Knowledge and Engineering} ({\bf TKDE}), 2022.

    \item \textbf{Binhui Xie}, Longhui Yuan, Shuang Li, Chi Harold Liu and Xinjing Cheng. \\
    Towards Fewer Annotations: Active Learning via Region Impurity and Prediction Uncertainty for Domain Adaptive Semantic Segmentation, \textit{IEEE Conference on Computer Vision and Pattern Recognition} ({\bf CVPR) \textcolor{red}{Oral Presentation}}, 2022, New Orleans, Louisiana, USA.

    \item Shuang Li, {\bf Binhui Xie}, Qiuxia Lin, Chi Harold Liu, Gao Huang and Guoren Wang. \\
    Generalized Domain Conditioned Network, \textit{IEEE Transactions on Pattern Analysis and Machine Intelligence} ({\bf \textcolor{red}{TPAMI}}), 44(8): 4093-4109 (2022).

    \item \textbf{Binhui Xie}, Longhui Yuan, Shuang Li, Chi Harold Liu, Xinjing Cheng and Guoren Wang. \\
    Active Learning for Domain Adaptation: An Energy-based Approach, \textit{AAAI Conference on Artificial Intelligence} ({\bf AAAI}), 2022, Virtual Conference.

    \item Shuang Li, Kaixiong Gong, \textbf{Binhui Xie}, Chi Harold Liu, Weipeng Cao, Song Tian. \\ 
    Critical Classes and Samples Discovering for Partial Domain Adaptation, \textit{IEEE Transactions on Cybernetics} ({\bf TCYB}), 2022.

    \item Shuang Li, Fangrui Lv, \textbf{Binhui Xie}, Chi Harold Liu, Jian Liang, Chen Qin. \\
    Bi-Classifier Determinacy Maximization for Unsupervised Domain Adaptation, \textit{AAAI Conference on Artificial Intelligence} ({\bf AAAI}), 2021, Virtual Conference.

    \item Shuang Li, \textbf{Binhui Xie}, Jiashu Wu, Ying Zhao, Chi Harold Liu, Zhengming Ding. \\
    Simultaneous Semantic Alignment Network for Heterogeneous Domain Adaptation, \textit{ACM Multimedia} ({\bf MM}), 2020, Virtual Conference.

    \item Shuang Li, Chi Harold Liu, Qiuxia Lin, \textbf{Binhui Xie}, Zhengming Ding, Gao Huang, Jian Tang. \\
    Domain Conditioned Adaptation Network, \textit{AAAI Conference on Artificial Intelligence} ({\bf AAAI}), 2020, New York, NY, USA.

    \item Shuang Li, Chi Harold Liu, \textbf{Binhui Xie}, Limin Su, Zhengming Ding, Gao Huang. \\
    Joint Adversarial Domain Adaptation, \textit{ACM Multimedia} ({\bf MM}), 2019, Nice, France.
    
    \item Shuang Li, Chi Harold Liu, Limin Su, \textbf{Binhui Xie}, Zhengming Ding, C. L. Philip Chen, Dapeng Wu. \\ Discriminative Transfer Feature and Label Consistency for Cross-Domain Image Classification, \textit{IEEE Transactions on Neural Networks and Learning Systems} ({\bf TNNLS}), 31(11): 4842-4856 (2020).
\end{enumerate}

\textbf{Technical Reports}
\begin{itemize}
    \item Yuxin Fang, Wen Wang, \textbf{Binhui Xie}, Quan Sun, Ledell Wu, Xinggang Wang, Tiejun Huang, Xinlong Wang, Yue Cao. EVA: Exploring the Limits of Masked Visual Representation Learning at Scale, arXiv:2211.07636.
    \item \textbf{Binhui Xie}, Shuang Li, Mingjia Li, Chi Harold Liu, Gao Huang, Guoren Wang. 
    SePiCo: Semantic-Guided Pixel Contrast for Domain Adaptive Semantic Segmentation, arXiv:2204.08808.
    \item \textbf{Binhui Xie}, Mingjia Li Shuang Li. 
    SPCL: A New Framework for Domain Adaptive Semantic Segmentation via Semantic Prototype-based Contrastive Learning, arXiv:2111.12358.
    \item Shuang Li, \textbf{Binhui Xie}, Bin Zang, Chi Harold Liu, Xinjing Cheng, Ruigang Yang, Guoren Wang. 
    Semantic Distribution-aware Contrastive Adaptation for Semantic Segmentation, arXiv:2105.05013. 
\end{itemize}
% Undergraduate's Thesis: Research on Generative Adversarial Networks Based Domain Adaptation, 2019.

%-----------EXPERIENCE-----------------
% \section{EXPERIENCE}
%   \resumeSubHeadingListStart

%     \resumeSubheading
%     {Lab of Intelligent and Network Computing, Beijing Institute of Technology}{Beijing, China}
%     {Research Assistant}{Oct 2018 - present}
%     \resumeItemListStart
%     \item\small{Research on domain adaptation algorithms for image classification and semantic segmentation tasks. \vspace{-2pt}}
%     \resumeItemListEnd

%   % \resumeSubheading
%   %   {Chengdu Neusoft University}{Chengdu, China}
%   %   {Software Engineer Internship}{Jun 2016 - Jul 2016}
%   %   \resumeItemListStart
%   %     \resumeItem{Java}
%   %       {Complete application development course by Chengdu Neusoft University. Implement Timetable app using Android Studio. Excel in communication and teamwork at start-up companies.}
%   %   \resumeItemListEnd

%   \resumeSubHeadingListEnd


% %-----------PROJECTS-----------------
% \section{Projects}
%   \resumeSubHeadingListStart
%     \resumeSubItem{QuantSoftware Toolkit}
%       {Open source python library for financial data analysis and machine learning for finance.}
%     \resumeSubItem{Github Visualization}
%       {Data Visualization of Git Log data using D3 to analyze project trends over time.}
%     \resumeSubItem{Recommendation System}
%       {Music and Movie recommender systems using collaborative filtering on public datasets.}
% %     \resumeSubItem{Mac Setup}
% %       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
%   \resumeSubHeadingListEnd

%-----------REVIEW SERVICES-----------------
\section{Academic Services}
\resumeSubHeadingListStart
\item \textbf{Organizer} of Workshop: VALSE 2022 (Student Workshop).

\item \textbf{Reviewer} for CVPR'23, ICLR'23, AAAI'23, ECCV'22, CVPR'22, AAAI'22, ICCV'21, CVPR'21, AAAI'21 etc.

\item \textbf{Reviewer} for TPAMI, TNNLS, TMM, etc.

%--------HONOR------------
\section{Honors}
 \resumeSubHeadingListStart
%  \item \textbf{CETC GUORUI Scholarship}, CETC, 2021.
  \item \textbf{Excellent Undergraduate}, Beijing Institute of Technology, 2019.
  %  \item \textbf{Second Class Scholarship}, Beijing Institute of Technology, 2018. \vspace{-2pt}
 \resumeSubHeadingListEnd


 %--------Talks------------
\section{Invited Talks}
\resumeSubHeadingListStart
  \item 2022.6, \textbf{ReadPaper}, Towards Fewer Annotations: Active Learning for Adaptive Semantic Segmentation. \vspace{-2pt} 
  \item 2022.6, \textbf{Synced}, Towards Fewer Annotations: Active Learning for Adaptive Semantic Segmentation. \vspace{-2pt} 
  \item 2022.5, \textbf{Zhidx Course}, Domain Adaptation meets Active Learning. \vspace{-2pt}  
  \item 2022.03, \textbf{AI Drive}, Energy-based Active Domain Adaptation. \vspace{-2pt}
  \item 2021.10, \textbf{VALSE}, Generalized Domain Conditioned Adaptation Network. \vspace{-2pt}
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
